---
title: "create_master"
author: "Matt Garcia"
output: html_document
---


# Loading of relevant libraries:

```{r setup, include=FALSE}
library(Lahman)
library(pitchRx)
library(dplyr)
library(dbplyr)
library(RSQLite)
library(gdata)
library(stringr)
library(readxl)
library(caret)
#library(xlsx)
```


# Creation of a SQLite database:

```{r}
db <- src_sqlite("pitchfx2018.sqlite3", create = T)
files <- c("inning/inning_hit.xml", "miniscoreboard.xml", "players.xml")
scrape(start = "2017-03-28", end = "2017-09-30", connect = db$con)
```


# Collecting master data:

```{r}
db <- src_sqlite("pitchfx2018.sqlite3", create = F)
atbats <- tbl(db, 'atbat')
  #select(batter_name, pitcher_name, event, stand, p_throws, atbat_des, event_num, num, gameday_link)
pitches <- tbl(db, 'pitch')
  #select(pitch_type, start_speed, px, pz, num, gameday_link)
master <- collect(inner_join(atbats, pitches, by = c('num', 'gameday_link')))
#master <- master %>%
#  distinct(batter_name, gameday_link, event_num, .keep_all = TRUE)
master <- master %>%
  mutate(grounders = ifelse(grepl('ground', atbat_des) | grepl('grounds', atbat_des), 1, 0)) %>%
  mutate(liners = ifelse(grepl('line', atbat_des) | grepl('lines', atbat_des), 1, 0)) %>%
  mutate(flies = ifelse(grepl('fly', atbat_des) | grepl('flies', atbat_des), 1, 0)) %>%
  mutate(singles = ifelse(event == 'Single', 1, 0)) %>%
  mutate(doubles = ifelse(event == 'Double', 1, 0)) %>%
  mutate(triples = ifelse(event == 'Triple', 1, 0)) %>%
  mutate(homeruns = ifelse(event == 'Home Run', 1, 0)) %>%
  mutate(walks = ifelse(event == 'Walk', 1, 0)) %>%
  mutate(strikeouts = ifelse(event == 'Strikeout' | event == 'Strikeout - DP', 1, 0)) %>%
  mutate(hitbypitch = ifelse(event == 'Hit By Pitch', 1, 0)) %>%
  mutate(intentional_walks = ifelse(event == 'Intent Walk', 1, 0)) %>%
  mutate(errors = ifelse(event == 'Field Error', 1, 0)) %>%
  mutate(interferences = ifelse(event == 'Catcher interference'| event == 'Batter interference' | event == 'Fan interference', 1, 0)) %>%
  mutate(sac_bunts = ifelse(event == 'Sac Bunt'| event == 'Sacrifice Bunt DP', 1, 0)) %>%
  mutate(sac_flies = ifelse(event == 'Sac Fly'| event == 'Sac Fly DP', 1, 0)) %>%
  mutate(outs = ifelse(event == 'Forceout' | event == 'Groundout' | event == 'Lineout' | event == 'Pop Out' | event == 'Flyout' | event == 'Grounded Into DP' | event == 'Bunt Groundout' | event == 'Bunt Lineout' | event == 'Bunt Pop Out' | event == 'Double Play' | event == 'Fielders Choice' | event == 'Fielders Choice Out' | event == 'Triple Play', 1, 0))
```


# Creating lists of hitters and pitchers with handedness:

```{r}
batter_handedness <- master %>%
  distinct(batter_name, .keep_all = TRUE) %>%
  select(batter_name, stand)

pitcher_handedness <- master %>%
  distinct(pitcher_name, .keep_all = TRUE) %>%
  select(pitcher_name, p_throws)
```


# Adding hitter stats:

```{r}
# vs all
hit_data <- master %>%
  group_by(batter_name) %>%
  filter(batter_name != 'N/A') %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks) + sum(intentional_walks), strikeouts = sum(strikeouts), hitbypitch = sum(hitbypitch), intentional_walks = sum(intentional_walks), errors = sum(errors), interferences = sum(interferences), sac_bunts = sum(sac_bunts), sac_flies = sum(sac_flies), outs = sum(outs), grounders = sum(grounders), liners = sum(liners), flies = sum(flies)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs) %>%
  mutate(plate_appearances = atbats + hitbypitch + walks - intentional_walks + errors + interferences + sac_bunts + sac_flies) %>%
  mutate(bip = singles + doubles + triples + homeruns + outs) %>%
  mutate(wOBA = (((.69 * walks) + (.72 * hitbypitch) + (.88 * singles) + (1.21 * doubles) + (1.53 * triples) + (1.97 * homeruns))/ (atbats + walks - intentional_walks + sac_flies + hitbypitch)))

hit_data <- hit_data %>%
  group_by(batter_name) %>%
  summarise(batter_BB = walks / plate_appearances, batter_K = strikeouts / plate_appearances, batter_BBK = walks / strikeouts, batter_AVG = (singles + doubles + triples + homeruns) / atbats, batter_OBP = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies), batter_SLG = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, batter_OPS = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies) + (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, batter_ISO = (2 * doubles + 3 * triples + 3 * homeruns) / atbats, batter_BABIP = (singles + doubles + triples) / (atbats - strikeouts - homeruns + sac_flies), batter_wRC = (((wOBA - .315) / 1.226) + .117) * plate_appearances, batter_wRAA = ((wOBA - .318) / 1.19) * plate_appearances, batter_wOBA = wOBA, batter_GBFB = grounders / flies, batter_GB = grounders / bip, batter_LD = liners / bip, batter_FB = flies / bip, batter_HRFB = homeruns / flies)

# vs right-handed pitchers
hit_datavsR <- master %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  filter(batter_name != 'N/A') %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks) + sum(intentional_walks), strikeouts = sum(strikeouts), hitbypitch = sum(hitbypitch), intentional_walks = sum(intentional_walks), errors = sum(errors), interferences = sum(interferences), sac_bunts = sum(sac_bunts), sac_flies = sum(sac_flies), outs = sum(outs), grounders = sum(grounders), liners = sum(liners), flies = sum(flies)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs) %>%
  mutate(plate_appearances = atbats + hitbypitch + walks - intentional_walks + errors + interferences + sac_bunts + sac_flies) %>%
  mutate(bip = singles + doubles + triples + homeruns + outs) %>%
  mutate(wOBAvsR = (((.69 * walks) + (.72 * hitbypitch) + (.88 * singles) + (1.21 * doubles) + (1.53 * triples) + (1.97 * homeruns))/ (atbats + walks - intentional_walks + sac_flies + hitbypitch)))

hit_datavsR <- hit_datavsR %>%
  group_by(batter_name) %>%
  summarise(batter_BBvsR = walks / plate_appearances, batter_KvsR = strikeouts / plate_appearances, batter_BBKvsR = walks / strikeouts, batter_AVGvsR = (singles + doubles + triples + homeruns) / atbats, batter_OBPvsR = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies), batter_SLGvsR = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, batter_OPSvsR = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies) + (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, batter_ISOvsR = (2 * doubles + 3 * triples + 3 * homeruns) / atbats, batter_BABIPvsR = (singles + doubles + triples) / (atbats - strikeouts - homeruns + sac_flies), batter_wRCvsR = (((wOBAvsR - .318) / 1.19) + .119) * plate_appearances, batter_wRAAvsR = ((wOBAvsR - .318) / 1.19) * plate_appearances, batter_wOBAvsR = wOBAvsR, batter_GBFBvsR = grounders / flies, batter_GBvsR = grounders / bip, batter_LDvsR = liners / bip, batter_FBvsR = flies / bip, batter_HRFBvsR = homeruns / flies)

# vs left-handed pitchers
hit_datavsL <- master %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  filter(batter_name != 'N/A') %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks) + sum(intentional_walks), strikeouts = sum(strikeouts), hitbypitch = sum(hitbypitch), intentional_walks = sum(intentional_walks), errors = sum(errors), interferences = sum(interferences), sac_bunts = sum(sac_bunts), sac_flies = sum(sac_flies), outs = sum(outs), grounders = sum(grounders), liners = sum(liners), flies = sum(flies)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs) %>%
  mutate(plate_appearances = atbats + hitbypitch + walks - intentional_walks + errors + interferences + sac_bunts + sac_flies) %>%
  mutate(bip = singles + doubles + triples + homeruns + outs) %>%
  mutate(wOBAvsL = (((.69 * walks) + (.72 * hitbypitch) + (.88 * singles) + (1.22 * doubles) + (1.56 * triples) + (2.04 * homeruns))/ (atbats + walks - intentional_walks + sac_flies + hitbypitch)))

hit_datavsL <- hit_datavsL %>%
  group_by(batter_name) %>%
  summarise(batter_BBvsL = walks / plate_appearances, batter_KvsL = strikeouts / plate_appearances, batter_BBKvsL = walks / strikeouts, batter_AVGvsL = (singles + doubles + triples + homeruns) / atbats, batter_OBPvsL = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies), batter_SLGvsL = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, batter_OPSvsL = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies) + (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, batter_ISOvsL = (2 * doubles + 3 * triples + 3 * homeruns) / atbats, batter_BABIPvsL = (singles + doubles + triples) / (atbats - strikeouts - homeruns + sac_flies), batter_wRCvsL = (((wOBAvsL - .318) / 1.24) + .112) * plate_appearances, batter_wRAAvsL = ((wOBAvsL - .318) / 1.24) * plate_appearances, batter_wOBAvsL = wOBAvsL, batter_GBFBvsL = grounders / flies, batter_GBvsL = grounders / bip, batter_LDvsL = liners / bip, batter_FBvsL = flies / bip, batter_HRFBvsL = homeruns / flies)


# combining for ease of use later
batter_stats <- collect(inner_join(hit_data, hit_datavsR, hit_datavsL, by = c('batter_name')))
batter_stats <- collect(inner_join(batter_stats, hit_datavsL, by = c('batter_name')))
```


# Adding pitcher stats:

```{r}
# vs all
pitch_data <- master %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks) + sum(intentional_walks), strikeouts = sum(strikeouts), hitbypitch = sum(hitbypitch), intentional_walks = sum(intentional_walks), errors = sum(errors), interferences = sum(interferences), sac_bunts = sum(sac_bunts), sac_flies = sum(sac_flies), outs = sum(outs), grounders = sum(grounders), liners = sum(liners), flies = sum(flies)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs) %>%
  mutate(plate_appearances = atbats + hitbypitch + walks - intentional_walks + errors + interferences + sac_bunts + sac_flies) %>%
  mutate(bip = singles + doubles + triples + homeruns + outs) %>%
  mutate(wOBA = (((.69 * walks) + (.72 * hitbypitch) + (.88 * singles) + (1.21 * doubles) + (1.53 * triples) + (1.97 * homeruns))/ (atbats + walks - intentional_walks + sac_flies + hitbypitch)))

pitch_data <- pitch_data %>%
  group_by(pitcher_name) %>%
  filter(pitcher_name != 'N/A') %>%
  summarise(pitcher_BB = walks / plate_appearances, pitcher_K = strikeouts / plate_appearances, pitcher_BBK = walks / strikeouts, pitcher_AVG = (singles + doubles + triples + homeruns) / atbats, pitcher_OBP = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies), pitcher_SLG = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, pitcher_OPS = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies) + (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, pitcher_ISO = (2 * doubles + 3 * triples + 3 * homeruns) / atbats, pitcher_BABIP = (singles + doubles + triples) / (atbats - strikeouts - homeruns + sac_flies), pitcher_FIP = (((13 * homeruns) + (3 * walks) - (2 * strikeouts)) / (atbats / 3)) + 3.10, pitcher_wOBA = wOBA, pitcher_GBFB = grounders / flies, pitcher_GB = grounders / bip, pitcher_LD = liners / bip, pitcher_FB = flies / bip, pitcher_HRFB = homeruns / flies, pitcher_WHIP = (walks + singles + doubles + triples + homeruns) / ((outs + strikeouts)/ 3), pitcher_HR9 = homeruns / ((outs + strikeouts)/ 27))

# vs right-handed hitters
pitch_datavsR <- master %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks) + sum(intentional_walks), strikeouts = sum(strikeouts), hitbypitch = sum(hitbypitch), intentional_walks = sum(intentional_walks), errors = sum(errors), interferences = sum(interferences), sac_bunts = sum(sac_bunts), sac_flies = sum(sac_flies), outs = sum(outs), grounders = sum(grounders), liners = sum(liners), flies = sum(flies)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs) %>%
  mutate(plate_appearances = atbats + hitbypitch + walks - intentional_walks + errors + interferences + sac_bunts + sac_flies) %>%
  mutate(bip = singles + doubles + triples + homeruns + outs) %>%
  mutate(wOBAvsR = (((.69 * walks) + (.72 * hitbypitch) + (.88 * singles) + (1.21 * doubles) + (1.53 * triples) + (1.97 * homeruns))/ (atbats + walks - intentional_walks + sac_flies + hitbypitch)))

pitch_datavsR <- pitch_datavsR %>%
  group_by(pitcher_name) %>%
  filter(pitcher_name != 'N/A') %>%
  summarise(pitcher_BBvsR = walks / plate_appearances, pitcher_KvsR = strikeouts / plate_appearances, pitcher_BBKvsR = walks / strikeouts, pitcher_AVGvsR = (singles + doubles + triples + homeruns) / atbats, pitcher_OBPvsR = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies), pitcher_SLGvsR = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, pitcher_OPSvsR = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies) + (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, pitcher_ISOvsR = (2 * doubles + 3 * triples + 3 * homeruns) / atbats, pitcher_BABIPvsR = (singles + doubles + triples) / (atbats - strikeouts - homeruns + sac_flies), pitcher_FIPvsR = (((13 * homeruns) + (3 * walks) - (2 * strikeouts)) / (atbats / 3)) + 3.10, pitcher_wOBAvsR = wOBAvsR, pitcher_GBFBvsR = grounders / flies, pitcher_GBvsR = grounders / bip, pitcher_LDvsR = liners / bip, pitcher_FBvsR = flies / bip, pitcher_HRFBvsR = homeruns / flies, pitcher_WHIPvsR = (walks + singles + doubles + triples + homeruns) / ((outs + strikeouts)/ 3), pitcher_HR9vsR = homeruns / ((outs + strikeouts)/ 27))

# vs left-handed hitters
pitch_datavsL <- master %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks) + sum(intentional_walks), strikeouts = sum(strikeouts), hitbypitch = sum(hitbypitch), intentional_walks = sum(intentional_walks), errors = sum(errors), interferences = sum(interferences), sac_bunts = sum(sac_bunts), sac_flies = sum(sac_flies), outs = sum(outs), grounders = sum(grounders), liners = sum(liners), flies = sum(flies)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs) %>%
  mutate(plate_appearances = atbats + hitbypitch + walks - intentional_walks + errors + interferences + sac_bunts + sac_flies) %>%
  mutate(bip = singles + doubles + triples + homeruns + outs) %>%
  mutate(wOBAvsL = (((.69 * walks) + (.72 * hitbypitch) + (.88 * singles) + (1.21 * doubles) + (1.53 * triples) + (1.97 * homeruns))/ (atbats + walks - intentional_walks + sac_flies + hitbypitch)))

pitch_datavsL <- pitch_datavsL %>%
  group_by(pitcher_name) %>%
  filter(pitcher_name != 'N/A') %>%
  summarise(pitcher_BBvsL = walks / plate_appearances, pitcher_KvsL = strikeouts / plate_appearances, pitcher_BBKvsL = walks / strikeouts, pitcher_AVGvsL = (singles + doubles + triples + homeruns) / atbats, pitcher_OBPvsL = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies), pitcher_SLGvsL = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, pitcher_OPSvsL = (singles + doubles + triples + homeruns + walks + hitbypitch) / (atbats + walks + hitbypitch + sac_flies) + (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats, pitcher_ISOvsL = (2 * doubles + 3 * triples + 3 * homeruns) / atbats, pitcher_BABIPvsL = (singles + doubles + triples) / (atbats - strikeouts - homeruns + sac_flies), pitcher_FIPvsL = (((13 * homeruns) + (3 * walks) - (2 * strikeouts)) / (atbats / 3)) + 3.10, pitcher_wOBAvsL = wOBAvsL, pitcher_GBFBvsL = grounders / flies, pitcher_GBvsL = grounders / bip, pitcher_LDvsL = liners / bip, pitcher_FBvsL = flies / bip, pitcher_HRFBvsL = homeruns / flies, pitcher_WHIPvsL = (walks + singles + doubles + triples + homeruns) / ((outs + strikeouts)/ 3), pitcher_HR9vsL = homeruns / ((outs + strikeouts)/ 27))

# combining for ease of use later
pitcher_stats <- collect(inner_join(pitch_data, pitch_datavsR, pitch_datavsL, by = c('pitcher_name')))
pitcher_stats <- collect(inner_join(pitcher_stats, pitch_datavsL, by = c('pitcher_name')))
```


# Creating hot zones:

```{r}
# Creation of hot zone 1:

zone1 <- master %>%
  filter(px >= -1) %>%
  filter(px <= -0.333) %>%
  filter(pz >= 2.8333) %>%
  filter(pz <= 3.5)

# Creation of hot zone 2:

zone2 <- master %>%
  filter(px >= -0.333) %>%
  filter(px <= 0.333) %>%
  filter(pz >= 2.8333) %>%
  filter(pz <= 3.5)

# Creation of hot zone 3:
    
zone3 <- master %>%
  filter(px >= 0.333) %>%
  filter(px <= 1) %>%
  filter(pz >= 2.8333) %>%
  filter(pz <= 3.5)
  
# Creation of hot zone 4:  
  
zone4 <- master %>%
  filter(px >= -1) %>%
  filter(px <= -0.333) %>%
  filter(pz >= 2.1666) %>%
  filter(pz <= 2.8333)
  
# Creation of hot zone 5:

zone5 <- master %>%
  filter(px >= -0.333) %>%
  filter(px <= 0.333) %>%
  filter(pz >= 2.1666) %>%
  filter(pz <= 2.8333)

# Creation of hot zone 6:

zone6 <- master %>%
  filter(px >= 0.333) %>%
  filter(px <= 1) %>%
  filter(pz >= 2.1666) %>%
  filter(pz <= 2.8333)
  
# Creation of hot zone 7:

zone7 <- master %>%
  filter(px >= -1) %>%
  filter(px <= -0.333) %>%
  filter(pz >= 1.5) %>%
  filter(pz <= 2.1666)
  
# Creation of hot zone 8:

zone8 <- master %>%
  filter(px >= -0.333) %>%
  filter(px <= 0.333) %>%
  filter(pz >= 1.5) %>%
  filter(pz <= 2.1666)
  
# Creation of hot zone 9:

zone9 <- master %>%
  filter(px >= 0.333) %>%
  filter(px <= 1) %>%
  filter(pz >= 1.5) %>%
  filter(pz <= 2.1666)

```


# Separating data in hot zones for batters and pitchers:

```{r}
# Hitters

hit_zone1_R <- zone1 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone1_R <- hit_zone1_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R1 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)

hit_zone2_R <- zone2 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone2_R <- hit_zone2_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R2 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(hit_zone1_R, hit_zone2_R, by = c('batter_name')))

hit_zone3_R <- zone3 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone3_R <- hit_zone3_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R3 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone3_R, by = c('batter_name')))

hit_zone4_R <- zone4 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone4_R <- hit_zone4_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R4 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone4_R, by = c('batter_name')))

hit_zone5_R <- zone5 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone5_R <- hit_zone5_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R5 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone5_R, by = c('batter_name')))

hit_zone6_R <- zone6 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone6_R <- hit_zone6_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R6 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone6_R, by = c('batter_name')))

hit_zone7_R <- zone7 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone7_R <- hit_zone7_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R7 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone7_R, by = c('batter_name')))

hit_zone8_R <- zone8 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone8_R <- hit_zone8_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R8 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone8_R, by = c('batter_name')))

hit_zone9_R <- zone9 %>%
  filter(p_throws == 'R') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone9_R <- hit_zone9_R %>%
  group_by(batter_name) %>%
  summarise(batter_vs_R9 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone9_R, by = c('batter_name')))

hit_zone1_L <- zone1 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone1_L <- hit_zone1_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L1 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone1_L, by = c('batter_name')))

hit_zone2_L <- zone2 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone2_L <- hit_zone2_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L2 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone2_L, by = c('batter_name')))

hit_zone3_L <- zone3 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone3_L <- hit_zone3_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L3 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone3_L, by = c('batter_name')))

hit_zone4_L <- zone4 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone4_L <- hit_zone4_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L4 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone4_L, by = c('batter_name')))

hit_zone5_L <- zone5 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone5_L <- hit_zone5_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L5 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone5_L, by = c('batter_name')))

hit_zone6_L <- zone6 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone6_L <- hit_zone6_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L6 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone6_L, by = c('batter_name')))

hit_zone7_L <- zone7 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone7_L <- hit_zone7_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L7 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone7_L, by = c('batter_name')))

hit_zone8_L <- zone8 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone8_L <- hit_zone8_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L8 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone8_L, by = c('batter_name')))

hit_zone9_L <- zone9 %>%
  filter(p_throws == 'L') %>%
  group_by(batter_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone9_L <- hit_zone9_L %>%
  group_by(batter_name) %>%
  summarise(batter_vs_L9 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
batters <- collect(inner_join(batters, hit_zone9_L, by = c('batter_name'))) %>%
  filter(batter_name != 'N/A')

# Pitchers

hit_zone1_pitch_R <- zone1 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone1_pitch_R <- hit_zone1_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R1 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)

hit_zone2_pitch_R <- zone2 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone2_pitch_R <- hit_zone2_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R2 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(hit_zone1_pitch_R, hit_zone2_pitch_R, by = c('pitcher_name')))

hit_zone3_pitch_R <- zone3 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone3_pitch_R <- hit_zone3_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R3 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone3_pitch_R, by = c('pitcher_name')))

hit_zone4_pitch_R <- zone4 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone4_pitch_R <- hit_zone4_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R4 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone4_pitch_R, by = c('pitcher_name')))

hit_zone5_pitch_R <- zone5 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone5_pitch_R <- hit_zone5_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R5 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone5_pitch_R, by = c('pitcher_name')))

hit_zone6_pitch_R <- zone6 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone6_pitch_R <- hit_zone6_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R6 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone6_pitch_R, by = c('pitcher_name')))

hit_zone7_pitch_R <- zone7 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone7_pitch_R <- hit_zone7_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R7 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone7_pitch_R, by = c('pitcher_name')))

hit_zone8_pitch_R <- zone8 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone8_pitch_R <- hit_zone8_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R8 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone8_pitch_R, by = c('pitcher_name')))

hit_zone9_pitch_R <- zone9 %>%
  filter(stand == 'R') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone9_pitch_R <- hit_zone9_pitch_R %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_R9 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone9_pitch_R, by = c('pitcher_name')))

hit_zone1_pitch_L <- zone1 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone1_pitch_L <- hit_zone1_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L1 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone1_pitch_L, by = c('pitcher_name')))

hit_zone2_pitch_L <- zone2 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone2_pitch_L <- hit_zone2_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L2 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone2_pitch_L, by = c('pitcher_name')))

hit_zone3_pitch_L <- zone3 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone3_pitch_L <- hit_zone3_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L3 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone3_pitch_L, by = c('pitcher_name')))

hit_zone4_pitch_L <- zone4 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone4_pitch_L <- hit_zone4_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L4 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone4_pitch_L, by = c('pitcher_name')))

hit_zone5_pitch_L <- zone5 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone5_pitch_L <- hit_zone5_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L5 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone5_pitch_L, by = c('pitcher_name')))

hit_zone6_pitch_L <- zone6 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone6_pitch_L <- hit_zone6_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L6 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone6_pitch_L, by = c('pitcher_name')))

hit_zone7_pitch_L <- zone7 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone7_pitch_L <- hit_zone7_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L7 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone7_pitch_L, by = c('pitcher_name')))

hit_zone8_pitch_L <- zone8 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone8_pitch_L <- hit_zone8_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L8 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone8_pitch_L, by = c('pitcher_name')))

hit_zone9_pitch_L <- zone9 %>%
  filter(stand == 'L') %>%
  group_by(pitcher_name) %>%
  summarise(singles = sum(singles), doubles = sum(doubles), triples = sum(triples), homeruns = sum(homeruns), walks = sum(walks), strikeouts = sum(strikeouts), outs = sum(outs)) %>%
  mutate(atbats = singles + doubles + triples + homeruns + strikeouts + outs)
hit_zone9_pitch_L <- hit_zone9_pitch_L %>%
  group_by(pitcher_name) %>%
  summarise(pitcher_vs_L9 = (singles + (2 * doubles) + (3 * triples) + (4 * homeruns)) / atbats)
pitchers <- collect(inner_join(pitchers, hit_zone9_pitch_L, by = c('pitcher_name'))) %>%
  filter(pitcher_name != 'N/A')

# Combining and organizing

hitter_hot_zone_ranks_vsR <- data.frame(batters, t(apply(-batters[2:10], 1, rank, ties.method='min')))

hitter_hot_zone_ranks_vsL <- data.frame(batters, t(apply(-batters[11:19], 1, rank, ties.method='min')))

batters <- collect(inner_join(hitter_hot_zone_ranks_vsR, hitter_hot_zone_ranks_vsL, by = c('batter_name')))

batters <- batters %>%
  select(batter_name, batter_vs_R1.1, batter_vs_R2.1, batter_vs_R3.1, batter_vs_R4.1, batter_vs_R5.1, batter_vs_R6.1, batter_vs_R7.1, batter_vs_R8.1, batter_vs_R9.1, batter_vs_L1.1, batter_vs_L2.1, batter_vs_L3.1, batter_vs_L4.1, batter_vs_L5.1, batter_vs_L6.1, batter_vs_L7.1, batter_vs_L8.1, batter_vs_L9.1)

pitcher_hot_zone_ranks_vsR <- data.frame(pitchers, t(apply(-pitchers[2:10], 1, rank, ties.method='min')))

pitcher_hot_zone_ranks_vsL <- data.frame(pitchers, t(apply(-pitchers[11:19], 1, rank, ties.method='min')))

pitchers <- collect(inner_join(pitcher_hot_zone_ranks_vsR, pitcher_hot_zone_ranks_vsL, by = c('pitcher_name')))

pitchers <- pitchers %>%
  select(pitcher_name, pitcher_vs_R1.1, pitcher_vs_R2.1, pitcher_vs_R3.1, pitcher_vs_R4.1, pitcher_vs_R5.1, pitcher_vs_R6.1, pitcher_vs_R7.1, pitcher_vs_R8.1, pitcher_vs_R9.1, pitcher_vs_L1.1, pitcher_vs_L2.1, pitcher_vs_L3.1, pitcher_vs_L4.1, pitcher_vs_L5.1, pitcher_vs_L6.1, pitcher_vs_L7.1, pitcher_vs_L8.1, pitcher_vs_L9.1)

colnames(batters)[colnames(batters)=="batter_vs_R1.1"] <- "BVR1"
colnames(batters)[colnames(batters)=="batter_vs_R2.1"] <- "BVR2"
colnames(batters)[colnames(batters)=="batter_vs_R3.1"] <- "BVR3"
colnames(batters)[colnames(batters)=="batter_vs_R4.1"] <- "BVR4"
colnames(batters)[colnames(batters)=="batter_vs_R5.1"] <- "BVR5"
colnames(batters)[colnames(batters)=="batter_vs_R6.1"] <- "BVR6"
colnames(batters)[colnames(batters)=="batter_vs_R7.1"] <- "BVR7"
colnames(batters)[colnames(batters)=="batter_vs_R8.1"] <- "BVR8"
colnames(batters)[colnames(batters)=="batter_vs_R9.1"] <- "BVR9"
colnames(batters)[colnames(batters)=="batter_vs_L1.1"] <- "BVL1"
colnames(batters)[colnames(batters)=="batter_vs_L2.1"] <- "BVL2"
colnames(batters)[colnames(batters)=="batter_vs_L3.1"] <- "BVL3"
colnames(batters)[colnames(batters)=="batter_vs_L4.1"] <- "BVL4"
colnames(batters)[colnames(batters)=="batter_vs_L5.1"] <- "BVL5"
colnames(batters)[colnames(batters)=="batter_vs_L6.1"] <- "BVL6"
colnames(batters)[colnames(batters)=="batter_vs_L7.1"] <- "BVL7"
colnames(batters)[colnames(batters)=="batter_vs_L8.1"] <- "BVL8"
colnames(batters)[colnames(batters)=="batter_vs_L9.1"] <- "BVL9"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R1.1"] <- "PVR1"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R2.1"] <- "PVR2"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R3.1"] <- "PVR3"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R4.1"] <- "PVR4"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R5.1"] <- "PVR5"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R6.1"] <- "PVR6"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R7.1"] <- "PVR7"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R8.1"] <- "PVR8"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_R9.1"] <- "PVR9"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L1.1"] <- "PVL1"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L2.1"] <- "PVL2"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L3.1"] <- "PVL3"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L4.1"] <- "PVL4"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L5.1"] <- "PVL5"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L6.1"] <- "PVL6"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L7.1"] <- "PVL7"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L8.1"] <- "PVL8"
colnames(pitchers)[colnames(pitchers)=="pitcher_vs_L9.1"] <- "PVL9"
```


# Joining all stats for each batter and pitcher:

```{r}
batter_stats <- collect(inner_join(batter_stats, batters, by = c('batter_name')))
pitcher_stats <- collect(inner_join(pitcher_stats, pitchers, by = c('pitcher_name')))
```


# Adding handedness for each batter and pitcher:

```{r}
batter_stats <- collect(inner_join(batter_stats, batter_handedness, by = c('batter_name')))
pitcher_stats <- collect(inner_join(pitcher_stats, pitcher_handedness, by = c('pitcher_name')))
```


# Collecting master data:

```{r}
# Creation of master data file:
db2 <- src_sqlite("pitchfx2018.sqlite3", create = F)
atbats2 <- tbl(db2, 'atbat')
  #select(batter_name, pitcher_name, event, stand, p_throws, atbat_des, event_num, num, gameday_link)
pitches2 <- tbl(db2, 'pitch')
  #select(pitch_type, start_speed, px, pz, num, gameday_link)
master2 <- collect(inner_join(atbats2, pitches2, by = c('num', 'gameday_link')))
#master <- master %>%
#  distinct(batter_name, gameday_link, event_num, .keep_all = TRUE)
master2 <- master2 %>%
  mutate(grounders = ifelse(grepl('ground', atbat_des) | grepl('grounds', atbat_des), 1, 0)) %>%
  mutate(liners = ifelse(grepl('line', atbat_des) | grepl('lines', atbat_des), 1, 0)) %>%
  mutate(flies = ifelse(grepl('fly', atbat_des) | grepl('flies', atbat_des), 1, 0)) %>%
  mutate(singles = ifelse(event == 'Single', 1, 0)) %>%
  mutate(doubles = ifelse(event == 'Double', 1, 0)) %>%
  mutate(triples = ifelse(event == 'Triple', 1, 0)) %>%
  mutate(homeruns = ifelse(event == 'Home Run', 1, 0)) %>%
  mutate(walks = ifelse(event == 'Walk', 1, 0)) %>%
  mutate(strikeouts = ifelse(event == 'Strikeout' | event == 'Strikeout - DP', 1, 0)) %>%
  mutate(hitbypitch = ifelse(event == 'Hit By Pitch', 1, 0)) %>%
  mutate(intentional_walks = ifelse(event == 'Intent Walk', 1, 0)) %>%
  mutate(errors = ifelse(event == 'Field Error', 1, 0)) %>%
  mutate(interferences = ifelse(event == 'Catcher interference'| event == 'Batter interference' | event == 'Fan interference', 1, 0)) %>%
  mutate(sac_bunts = ifelse(event == 'Sac Bunt'| event == 'Sacrifice Bunt DP', 1, 0)) %>%
  mutate(sac_flies = ifelse(event == 'Sac Fly'| event == 'Sac Fly DP', 1, 0)) %>%
  mutate(outs = ifelse(event == 'Forceout' | event == 'Groundout' | event == 'Lineout' | event == 'Pop Out' | event == 'Flyout' | event == 'Grounded Into DP' | event == 'Bunt Groundout' | event == 'Bunt Lineout' | event == 'Bunt Pop Out' | event == 'Double Play' | event == 'Fielders Choice' | event == 'Fielders Choice Out' | event == 'Triple Play', 1, 0))
```


# Adding in outcome of at-bat (home run or no home run) for pitcher vs batter:

```{r}
home_runs <- master2 %>%
  select(batter_name, pitcher_name, event)
home_runs <- home_runs %>%
  distinct(batter_name, pitcher_name, atbat_des, tfs_zulu, gameday_link, event, .keep_all = TRUE)
```
```{r}
home_runs$event <- ifelse(home_runs$event == "Home Run", "YES", "NO")
home_runs$event <- factor(home_runs$event, levels = c("YES", "NO"))

home_run_data <- collect(inner_join(batter_stats, home_runs, by = c('batter_name')))
home_run_data <- collect(inner_join(home_run_data, pitcher_stats, by = c('pitcher_name')))
```


# Adding split stats for each matchup (based on handedness):

```{r}
endend <- home_run_data %>%
  mutate(split_batter_BB = ifelse(p_throws == "R", batter_BBvsR, batter_BBvsL)) %>%
  mutate(split_batter_K = ifelse(p_throws == "R", batter_KvsR, batter_KvsL)) %>%
  mutate(split_batter_AVG = ifelse(p_throws == "R", batter_AVGvsR, batter_AVGvsL)) %>%
  mutate(split_batter_OBP = ifelse(p_throws == "R", batter_OBPvsR, batter_OBPvsL)) %>%
  mutate(split_batter_SLG = ifelse(p_throws == "R", batter_SLGvsR, batter_SLGvsL)) %>%
  mutate(split_batter_ISO = ifelse(p_throws == "R", batter_ISOvsR, batter_ISOvsL)) %>%
  mutate(split_batter_wRC = ifelse(p_throws == "R", batter_wRCvsR, batter_wRCvsL)) %>%
  mutate(split_batter_wRAA = ifelse(p_throws == "R", batter_wRAAvsR, batter_wRAAvsL)) %>%
  mutate(split_batter_wOBA = ifelse(p_throws == "R", batter_wOBAvsR, batter_wOBAvsL)) %>%
  mutate(split_batter_GB = ifelse(p_throws == "R", batter_GBvsR, batter_GBvsL)) %>%
  mutate(split_batter_LD = ifelse(p_throws == "R", batter_LDvsR, batter_LDvsL)) %>%
  mutate(split_batter_FB = ifelse(p_throws == "R", batter_FBvsR, batter_FBvsL)) %>%
  mutate(split_batter_HRFB = ifelse(p_throws == "R", batter_HRFBvsR, batter_HRFBvsL)) %>%
  mutate(split_pitcher_BB = ifelse(stand == "R", pitcher_BBvsR, pitcher_BBvsL)) %>%
  mutate(split_pitcher_K = ifelse(stand == "R", pitcher_KvsR, pitcher_KvsL)) %>%
  mutate(split_pitcher_AVG = ifelse(stand == "R", pitcher_AVGvsR, pitcher_AVGvsL)) %>%
  mutate(split_pitcher_OBP = ifelse(stand == "R", pitcher_OBPvsR, pitcher_OBPvsL)) %>%
  mutate(split_pitcher_SLG = ifelse(stand == "R", pitcher_SLGvsR, pitcher_SLGvsL)) %>%
  mutate(split_pitcher_ISO = ifelse(stand == "R", pitcher_ISOvsR, pitcher_ISOvsL)) %>%
  mutate(split_pitcher_WHIP = ifelse(stand == "R", pitcher_WHIPvsR, pitcher_WHIPvsL)) %>%
  mutate(split_pitcher_FIP = ifelse(stand == "R", pitcher_FIPvsR, pitcher_FIPvsL)) %>%
  mutate(split_pitcher_GB = ifelse(stand == "R", pitcher_GBvsR, pitcher_GBvsL)) %>%
  mutate(split_pitcher_LD = ifelse(stand == "R", pitcher_LDvsR, pitcher_LDvsL)) %>%
  mutate(split_pitcher_FB = ifelse(stand == "R", pitcher_FBvsR, pitcher_FBvsL)) %>%
  mutate(split_pitcher_HRFB = ifelse(stand == "R", pitcher_HRFBvsR, pitcher_HRFBvsL)) %>%
  mutate(HZ_Score = ifelse(p_throws == "R", ifelse(stand=="R", (BVR1-PVR1)^2 + (BVR2-PVR2)^2 + (BVR3-PVR3)^2 + (BVR4-PVR4)^2 + (BVR5-PVR5)^2 + (BVR6-PVR6)^2 + (BVR7-PVR7)^2 + (BVR8-PVR8)^2 + (BVR9-PVR9)^2, (BVR1-PVL1)^2 + (BVR2-PVL2)^2 + (BVR3-PVL3)^2 + (BVR4-PVL4)^2 + (BVR5-PVL5)^2 + (BVR6-PVL6)^2 + (BVR7-PVL7)^2 + (BVR8-PVL8)^2 + (BVR9-PVL9)^2), ifelse(stand=="R", (BVL1-PVR1)^2 + (BVL2-PVR2)^2 + (BVL3-PVR3)^2 + (BVL4-PVR4)^2 + (BVL5-PVR5)^2 + (BVL6-PVR6)^2 + (BVL7-PVR7)^2 + (BVL8-PVR8)^2 + (BVL9-PVR9)^2, (BVL1-PVL1)^2 + (BVL2-PVL2)^2 + (BVL3-PVL3)^2 + (BVL4-PVL4)^2 + (BVL5-PVL5)^2 + (BVL6-PVL6)^2 + (BVL7-PVL7)^2 + (BVL8-PVL8)^2 + (BVL9-PVL9)^2))) %>%
  select(batter_name, batter_BB, batter_K, batter_AVG, batter_OBP, batter_SLG, batter_ISO, batter_wRC, batter_wRAA, batter_wOBA, batter_LD, batter_FB, batter_HRFB, pitcher_BB, pitcher_K, pitcher_AVG, pitcher_OBP, pitcher_SLG, pitcher_ISO, pitcher_WHIP, pitcher_FIP, pitcher_LD, pitcher_FB, pitcher_HRFB, split_batter_BB, split_batter_K, split_batter_AVG, split_batter_OBP, split_batter_SLG, split_batter_ISO, split_batter_wRC, split_batter_wRAA, split_batter_wOBA, split_batter_LD, split_batter_FB, split_batter_HRFB, split_pitcher_BB, split_pitcher_K, split_pitcher_AVG, split_pitcher_OBP, split_pitcher_SLG, split_pitcher_ISO, split_pitcher_WHIP, split_pitcher_FIP, split_pitcher_LD, split_pitcher_FB, split_pitcher_HRFB, HZ_Score, event)
endend <- na.omit(endend)
endend <- endend %>%
  filter(pitcher_WHIP != Inf) %>%
  filter(split_batter_HRFB != Inf) %>%
  filter(split_pitcher_HRFB != Inf) %>%
  filter(batter_HRFB != Inf) %>%
  filter(pitcher_HRFB != Inf) %>%
  filter(pitcher_WHIP != Inf) %>%
  filter(split_pitcher_WHIP != Inf)
```


# Writing to CSV

```{r}
write.csv(endend, 'master.csv')
write.csv(batter_stats, 'batter_stats.csv')
write.csv(pitcher_stats, 'pitcher_stats.csv')
```


